Random Forests", OAs

### 2024-09-11 src/oa_RF_corrected_10.Rmd
oa corrected 10

# correct for non-England file names
df <- df %>% 
  mutate(RGN11CD = ifelse(RGN11CD == "Wales", "W0",
                          ifelse(RGN11CD == "Scotland", "S1",
                                 ifelse(RGN11CD == "NI", "N0", RGN11CD))))

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  rename(RGN11CD = RGN21CD) %>% 
  add_row(RGN11CD = c("S1", "N0", "W0"), 
          RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))

>>>>

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  rename(RGN11CD = RGN21CD) %>% 
  add_row(RGN11CD = c("Scotland", "NI", "Wales"),
          RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))
